A quantitative framework for investigating the reliability of empirical network construction

### 2018-11-29 manuscript/reply_to_reviewers.tex

	2/ network oversight: the approach considers that the interactions are independent, which is not the case in real data. Indeed, the paper is supposed to be “network-oriented“ but the methodology deals with independent interactions (e.g. the variables L,T,X and D introduced lines 62,77,101 are for instance not indexed by ij which could have suggested that the interactions were seen as a whole). Consequently, the mathematical framework remains quite simple and may not reflect nor model the processes governing the actual detection of interactions. Despite of this drawback, the proposed method is interesting but at least the authors should add some discussion on the limits of dealing with independent interactions,

	3/ identifiability: the reader would appreciate that the authors discuss and prove the identifiability of the model. Indeed, the three levels of uncertainity are nested but one could wonder whether different parameters at the three levels can fit the same data with the same quality (i.e. no identifiability).  I would suggest this point to be addressed in a specific section.

	4/ absence of simulations: the authors proposed an original approach based on a bayesian framework. Beyond the identifiability question (see above), the reader can question the power of the method. Usually, a methodological proposal comes with a complete simulation study that is supposed to show  the proposed model is adapted/suitable to the question and efficient to solve it. In the paper in its present form, the authors assume that the reader will be convinced by the results obtained on a single real dataset… In my opinion, the reader can’t be fairly convinced: how powerfull is the method? what can we say about the priors? how much data (n, k) is necessary to expect good results? An so on… Only a well-conducted simulation study can answer these questions.

	5/ results\&discussion too short: the reader is surprised to read 27 lines of raw results only… Given the amount of new methodology that is proposed, one can expect a complete description of its pros and cons. Obvisouly, a simulation study (see above) would enrich the results part. Forgetting about the length of these parts, it is still difficult to catch the key messages from the text, and it is not obvious to relate discussion and the obtained results (for instance,from l.343 to l.351).

	6/ lack of rigorous notations: it is possible to understand the approach with the present notations but some improvements can help the reader because there are a series of inconsistencies. Here are some suggestions. The authors chose upper case letters L,T ,X,D for single entities whereas the mathematician is used to expect matrices or constants in upper case. Traditionaly, given species i and j, we would consider interaction $L_ij$, feasibility $X_ij$, detectionability $D_ij$...
	Still, what is T?? not defined, never reused: is it a characteristics on i, on j, on both?
	How can be D<1 on l.169? D=0 or 1 since it says if an interaction is detectable or not...
	Moreover, L is reused later but is the number of interactions (l.100 supp.mat)…
	What is “N” in Figure 4? is it “n”? What is $n_ij$ and $k_ij$ l.266? Never defined, never reused.
	In the beginning of the paper, $\lambda$ is a probability (l.62) but it becomes a random variable (l.164): it would be more consistent to introduce before the notion of hyperparameters  (l.209-213) and to explain we consider that $\lambda$ is drawn into its distribution.

### 2019-01-10 manuscript/reply_to_reviewers.tex

% Ask for help: how would we expand this to interaction frequencies? Still with the Bernoulli? Worthwhile to add a demo of Jensen's inequality?
% To do: expand discussion of our results as much as possible given space constraints.
% -----------------------------------------------------------------------------
% -----------------------------------------------------------------------------
{\Large \bf Reply to Associate Editor}
% ---------------------------------------

	\begin{refquote}
	Your manuscript has been assessed by four different referees who agree that you touch upon a very important problem. However, they all feel your manuscript needs substantial improvements. They provide excellent advise on how to revise your manuscript and you should carefully consider all their comments. Overall, you do not acknowledge important past contributions and do not clearly explain the importance of the methodological issues you cover in your study. Importantly, referee 1 feels the real novelty of your study is the consideration of the importance and complexity of choosing prior information in constructing networks. Obviously, this is an issue in the context of Bayesian approaches, which are not necessarily well understood by empiricists, precisely the audience your manuscript should address. Please, follow very closely the suggestions of the referees when revising your manuscript.

	\end{refquote}

	\textbf{R:} We appreciate the thoughtful feedback by the four referees. We take particular note of the comments regarding the structure and grounding of our introduction and have worked to address them.

	Reviewer 2 takes a different view of the purpose and scope of the manuscript from that of the other reviewers. We respect his/her ideas but feel that some are beyond the scope of the present manuscript. In particular, we do not feel that a full simulation study is necessary given the simplicity of our framework. We emphasize that we are not introducing a software package (although we do provide simple code to aid those who are new to the field), nor are we introducing an entirely new framework (as the other Reviewers point out, many components of our approach have been touched on by previous work). Thus, the novelty and impact of our work explicitly lies in connecting a Bayesian statistical approach to the problem of limited and uneven sampling of networks (driven by difference in species abundances, detectabilities, constrained time and budgets, etc.) and, we hope, in making this method more accessible to those without extensive statistical or modelling experience. Please note that Reviewer 3 identified this need explicitly. 
	% Tomas has a line break here, I'm not sure.
	Because of the difference between Reviewer 2 and the other Reviewers, we have opted to prioritise the majority view and focused first on comments by Reviewers 1, 3, and 4. However, we hope and trust that, in the course of these revisions, we have at least partially addressed Reviewer 2's concerns as well.

	As a key point of departure for our revision, we have taken Reviewer 1's suggestion that we expand upon the different types of priors available and reasons for choosing one over the other. We also now offer a brief discussion about concerns over the subjectivity of prior selection. We argue that a great deal of subjectivity is baked into the compilation of empirical networks and that a Bayesian approach can be seen as making this subjectivity explicit. We hope that this will encourage empiricists to explicitly use their system-specific knowledge to create reasonable priors, as likely already occurs subconsciously (as in the designation of "forbidden links").

	Overall, we hope that our revision more clearly frames the importance of uncertainty in ecological networks and positions a simple Bayesian approach as a partial solution (together with high-quality sampling, of course). 
	We have also added many references to prior work. While the present study is not intended to be a full review of the literature, we certainly do not wish to downplay other workers in the area.
	Finally, several of the Reviewers appeared to believe that we were advocating for reduced sampling effort. That is emphatically not the case (we find the idea absurd), and we have revised the manuscript to be clearer about the fact that increased sampling effort can reduce some sources of uncertainty. We hope that it is now clear that the Bayesian framework we promote is a complement to high sampling effort.

### 2019-01-11 manuscript/CI_interactions.tex
integrating Tomas' comments to reply

    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007,Jordano2016}). An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to correctly document interactions than species~\citep{Guimera2009,Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}. As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Bartomeeus2013,Poisot2016}. Efforts in this vein usually take the form of creating model food webs that approximate observed empirical networks~\citep{Allesina2008,Guimera2009,Williams2010,Rohr2016}. These models may be based on species traits and/or abundances~\citep{Rohr2016,Weinstein2017,Weinstein2017a,Graham2018} or on simple abstract rules~\citep{Allesina2008,Guimera2009,Williams2010}. Such models provide an important ''reality check'' by allowing us to test hypotheses about the factors structuring ecological networks~\citep{Bartomeus2013,Weinstein2017.Weinstein2017a,Graham2018}. They can also allow us to estimate the numbers of interactions which have not been observed~\citep{Jordano2016,Weinstein2017a} and predict which unobserved interactions are most likely~\citep{Guimera2009,Bartomeus2013}.

    [[These two paragraphs try to frame our study more clearly]]
    To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2013}) or very system-specific (e.g.,~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}); in either case one of these models may be a poor fit for a particular study system. Moreover, some of the system-specific models described above cannot accommodate species observed only once~\citep{Bartomeus2013,Weinstein2017}. As rare species are likely to be observed less frequently~\citep{Bluthgen2010} and may be of particular interest (e.g., when modelling species loss), there is a need for a more widely-applicable framework that includes such rare species.

    Here we introduce a simple Bayesian framework that can easily be adapted to different systems. First, we provide a brief description of the nested levels of uncertainty affecting ecological network construction. In the context of this uncertainty, which can be reduced but not eliminated by high-quality sampling (\citealp[see Box 1]{Bartomes2013}), we present our Bayesian framework for combining observed data with a prior expectation of network structure. We conclude with a worked example applying this framework to an intensively-sampled host-parasitoid network. We find that even the highest-quality empirical network we could find had substantial uncertainty about whether many pairs of species interact, demonstrating the need to include information about this uncertainty in published networks. We also show that this interaction-level uncertainty leads to uncertainty about estimates of network structure, with important implications for comparisons across networks; especially those compiled with different sampling intensity~\citep{Weinstein2017}.

@@

            Both whether species can interact and whether they do interact at a particular place and time have been discussed in the context of "forbidden links"~\citep{Jordano2016}. In this framework, all links which are prevented by spatio-temporal uncoupling~\citep{Jordano1987}, physiological constraints~\citep{Jordano1987,More2012}, etc. are considered "structural zeros" that cannot be observed~\citep{Jordano2016}. We conceptually distinguish between physiological constraints and spatio-temporal uncoupling to allow for cases in which a species is introduced to a new habitat, expands its range, or shifts phenology~\citep{Gravel2013}. In such cases, links which are forbidden due to physiological constraints remain forbidden but links previously forbidden due to spatio-temporal mismatch could potentially occur.

@@

          Some types of interactions will have higher detection uncertainty than others. Pollination, for example, occurs briefly and does not leave long-lasting evidence, while parasitism can be a lifelong association between species. Even long-term interactions can be missed, however, especially if species are difficult to identify or if not all individuals of a species share the interaction~\citep{Wells2013,Cirtwill2016}. Parasites, for example, are often concentrated in only a few individuals~\citep{Lagrue2017}. If these infected individuals do not happen to be included in a sample, their interactions will be missed. Detection probabilities also vary widely between species, and potentially individuals within species, due to different abundances and behaviours~\citep{Wells2013,Weinstein2017}.

@@

        If a similar dataset is not available, it is also possible to use data from the study at hand to develop a prior (i.e., "approximate Bayes"~\citet{Gelmanblog})~\citep{Casella1985,Spiegelhalter2000}. This approach is used in medical testing~\citep{Copas1972,Spiegelhalter2000} and disease modelling~\citep{Leyland2005,Brooks2015} using information from pilot studies and can easily be applied to ecological systems. Returning to the example of degree distributions, this approach allows us to use information from abundant and easily-sampled species to predict interaction probabilities for species which were observed only rarely. Despite its practicality, empirical Bayes has been criticized for being overly subjective~\citep{Berger2006} and because estimating hyperparameters from data serves as an approximation of some true hyperparameters which remain unknown~\citep{Gelmanblog}. We therefore encourage researchers to carefully consider whether external data or an appropriate trait model is available before opting for a prior based on some of their own data. Nevertheless, there are likely to be many situations where approximate Bayes provides the best way to describe the uncertainty in the dataset. We illustrate this approach in the following empirical example.

@@

      Researchers are often interested in measures of network structure rather than the network itself. Computing most network metrics is straightforward when the different $\lambda$ of the adjacency matrix are known and assumed not to vary~\citep{Poisot2016}. Incorporating variance in $\lambda$ into these calculations, however, is not so easy. Computation of these metrics involves non-linear functions. By Jensen's inequality~\citep{Jensen1906}, this means that the average of a network metric (a function of stochastic interactions) is not the same as the network metric calculated based on the average interaction probability. Thus, any uncertainty in the values of $\lambda$ could bias both the mean and variance of network metrics, giving misleading results (simulated in \emph{Appendix S1}). One way to avoid this situation is to calculate the properties of a suite of simulated networks~\citep{Vazquez2005,Guimera209}.

@@

  \begin{figure}[h!]
    \caption{Imperfect detection of interactions increases the number of samples required to be confident that an interaction never occurs. Assume that two species cannot interact (i.e., $\lambda=0$) and that the number of observed interactions follows a binomial distribution depending upon the number of observed interactions $k$ and observed co-occurrances $n$. The maximum likelihood estimate (MLE) for $\lambda$ is $\lambda_{MLE}=\frac{k}{n}$. Note that $\lambda$ is not a point estimate but rather a random variable with an unknown distribution. This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact. Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact.\\
    Importantly, we can estimate the variance of $\lambda$ as well as the MLE; available methods include the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]).
    Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for the interaction probability $\lambda$ for a pair of species that has been observed co-occurring $n$ times but never interacting ($k = 0$). The upper limit of the credible interval only reaches 0.1 (dashed, red line) with 35 observations. Thus, adding more observations is useful in controlling uncertainty, but the number of observations added must be very high unless we have some other reason to believe that an interaction cannot occur (i.e., a strong prior).}
    \label{upper_limits}
    \begin{center}
    \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
    % \includegraphics*[width=.8\textwidth]{Figure_3.eps}
    \end{center}
    \end{figure}

>>>>

    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007,Jordano2016}). An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to correctly document interactions than species~\citep{Guimera2009,Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}. As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Bartomeus2013,Poisot2016}. Efforts in this vein usually take the form of creating model food webs that approximate observed empirical networks~\citep{Allesina2008,Guimera2009,Williams2010,Rohr2016}. These models may be based on species traits and/or abundances~\citep{Rohr2016,Weinstein2017,Weinstein2017a,Graham2018} or on simple abstract rules~\citep{Allesina2008,Guimera2009,Williams2010}. Such models provide an important ''reality check'' by allowing us to test hypotheses about the factors structuring ecological networks~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}. They can also allow us to estimate the numbers of interactions which have not been observed~\citep{Jordano2016,Weinstein2017a} and predict which unobserved interactions are most likely~\citep{Guimera2009,Bartomeus2013}.

    [[These two paragraphs try to frame our study more clearly]]
    To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2013}) or very system-specific (e.g.,~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}); in either case one of these models may be a poor fit for a particular study system. Moreover, some of the system-specific models described above cannot accommodate species observed only once~\citep{Bartomeus2013,Weinstein2017}. As rare species are likely to be observed less frequently~\citep{Bluthgen2006} and may be of particular interest (e.g., when modelling species loss), there is a need for a more widely-applicable framework that includes such rare species.

    Here we introduce a simple Bayesian framework that can easily be adapted to different systems. First, we provide a brief description of the nested levels of uncertainty affecting ecological network construction. In the context of this uncertainty, which can be reduced but not eliminated by high-quality sampling (\citealp[see Box 1]{Bartomeus2013}), we present our Bayesian framework for combining observed data with a prior expectation of network structure. We conclude with a worked example applying this framework to an intensively-sampled host-parasitoid network. We find that even the highest-quality empirical network we could find had substantial uncertainty about whether many pairs of species interact, demonstrating the need to include information about this uncertainty in published networks. We also show that this interaction-level uncertainty leads to uncertainty about estimates of network structure, with important implications for comparisons across networks; especially those compiled with different sampling intensity~\citep{Weinstein2017}.

@@

            Both whether species can interact and whether they do interact at a particular place and time have been discussed in the context of "forbidden links"~\citep{Jordano2016}. In this framework, all links which are prevented by spatio-temporal uncoupling, physiological constraints, etc. are considered "structural zeros" that cannot be observed~\citep{Jordano1987,Jordano2016}. We conceptually distinguish between physiological constraints and spatio-temporal uncoupling to allow for cases in which a species is introduced to a new habitat, expands its range, or shifts phenology~\citep{Gravel2013}. In such cases, links which are forbidden due to physiological constraints remain forbidden but links previously forbidden due to spatio-temporal mismatch could potentially occur.

@@

          Some types of interactions will have higher detection uncertainty than others. Pollination, for example, occurs briefly and does not leave long-lasting evidence, while parasitism can be a lifelong association between species. Even long-term interactions can be missed, however, especially if species are difficult to identify or if not all individuals of a species share the interaction~\citep{Wells2013,Cirtwill2016}. Parasites, for example, are often concentrated in only a few individuals~\citep{Lagrue2015}. If these infected individuals do not happen to be included in a sample, their interactions will be missed. Detection probabilities also vary widely between species, and potentially individuals within species, due to different abundances and behaviours~\citep{Wells2013,Weinstein2017}.

@@

        If a similar dataset is not available, it is also possible to use data from the study at hand to develop a prior (i.e., "approximate Bayes"~\citet{Gelmanblog})~\citep{Casella1985,Spiegelhalter2000}. This approach is used in medical testing~\citep{Copas1972,Spiegelhalter2000} and disease modelling~\citep{Leyland2005,Brooks2015} using information from pilot studies and can easily be applied to ecological systems. Returning to the example of degree distributions, this approach allows us to use information from abundant and easily-sampled species to predict interaction probabilities for species which were observed only rarely. Despite its practicality, approximate Bayes has been criticized for being overly subjective~\citep{Berger2006} and because estimating hyperparameters from data serves as an approximation of some true hyperparameters which remain unknown~\citep{Gelmanblog}. We therefore encourage researchers to carefully consider whether external data or an appropriate trait model is available before opting for a prior based on some of their own data. Nevertheless, there are likely to be many situations where approximate Bayes provides the best way to describe the uncertainty in the dataset. We illustrate this approach in the following empirical example.

@@

      Researchers are often interested in measures of network structure rather than the network itself. Computing most network metrics is straightforward when the different $\lambda$ of the adjacency matrix are known and assumed not to vary~\citep{Poisot2016}. Incorporating variance in $\lambda$ into these calculations, however, is not so easy. Computation of these metrics involves non-linear functions. By Jensen's inequality~\citep{Jensen1906}, this means that the average of a network metric (a function of stochastic interactions) is not the same as the network metric calculated based on the average interaction probability. Thus, any uncertainty in the values of $\lambda$ could bias both the mean and variance of network metrics, giving misleading results (simulated in \emph{Appendix S1}). One way to avoid this situation is to calculate the properties of a suite of simulated networks~\citep{Vazquez2005,Guimera2009}.

@@

  \begin{figure}[h!]
    \caption{Imperfect detection of interactions increases the number of samples required to be confident that an interaction never occurs. Assume that two species cannot interact (i.e., $\lambda=0$) and that the number of observed interactions follows a binomial distribution depending upon the number of observed interactions $k$ and observed co-occurrances $n$. The maximum likelihood estimate (MLE) for $\lambda$ is $\lambda_{MLE}=\frac{k}{n}$. Note that $\lambda$ is not a point estimate but rather a random variable with an unknown distribution. This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact. Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact.\\
    Importantly, we can estimate the variance of $\lambda$ as well as the MLE; available methods include the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]). The distribution of the MLE for $\lambda$ thus obtained is a key part of the Bayesian distribution for $\lambda$.
    Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for the interaction probability $\lambda$ for a pair of species that has been observed co-occurring $n$ times but never interacting ($k = 0$). The upper limit of the credible interval only reaches 0.1 (dashed, red line) with 35 observations. Thus, adding more observations is useful in controlling uncertainty, but the number of observations added must be very high unless we have some other reason to believe that an interaction cannot occur (i.e., a strong prior).}
    \label{upper_limits}
    \begin{center}
    \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
    % \includegraphics*[width=.8\textwidth]{Figure_3.eps}
    \end{center}
    \end{figure}
